Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-26 paper.tex
update

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.9]{beramono}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{listings}
\usepackage{paralist}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{flushend}

@@

In traditional $k$-CFA algorithm and the AAM we showed in section \ref{aam}, 
the return-flow of invocation @(id 2)@
is going to both call-sites @(id 1)@ and @(id 1)@. Therefore, the
returned value @2@ for variable @y@ is also propagated to 
variable @x@ and then imprecise analysis result is arose.
This return-flow merging is inevitable even we increase the context-sensitivity.
If we use the monovariant analysis 0CFA, the analyzing result would be @x@ and 
@y@ point to set @\{1, 2\}@, because it not distinguishes
@z@ at different call-sites.
Under $1$-CFA, the algorithm is able to distinguish that variable @z@ of function
@id@ has two different values at two call-sites, so variable @y@ 
would not be polluted by @1@, but it is still helplessness for distinguish
return-flows.
TODO: do need more details to explain this example? (as in P4F paper)

@@

@f1@ and @f2@ call each others, and the stack will be interleaved
pushing @f1@ and @f2@ onto the top of current stack, but not existing 
two stack components are identical in the state space.

@@

Recent years, there are great efforts \cite{vardoulakis2010cfa2, earl2012introspective, 
gilray2016pushdown, johnson2015abstracting} to achieve precise call/return 
match based on small-step AAM which is what we described in section \ref{aam}.

@@

\textbf{Pushdown for Free.}
\citeauthor{gilray2016pushdown} proposed a continuation address allocator for 
small-step abstracting abstract machine that is both easy to implement and
computational inexpensive.

@@

@@

On the other side, with the insight from Reynold that the defined language will inherit properties
from the defining language, \citeauthor{darais2017abstracting} construct abstracting 
definitional interpreters (ADI) that automatically inherit the pushdown control-flow 
property from the defining language.
TODO: connection to this paper.
TODO: although they establish pushdown control-flow analysis in different ways, 
is there a correspondence between different methods?

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.85]{beramono}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{listings}
\usepackage{paralist}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{flushend}

@@

In traditional $k$-CFA algorithm and the AAM we showed in section \ref{aam}, 
the return-flow of invocation @(id 2)@
is going to both call-sites @(id 1)@ and @(id 2)@. Therefore, the
returned value @2@ for variable @y@ is also propagated to 
variable @x@ and then imprecise analysis result is arose.
This return-flow merging is inevitable even we increase the context-sensitivity.
If we use the monovariant analysis (i.e. 0CFA), the analyzing result would be @x@ and 
@y@ point to set @{1, 2}@, because the algorithm not distinguishes
@z@ comes from different call-sites.
Under $1$-CFA, the algorithm is able to distinguish that variable @z@ of function
@id@ has two different values at two call-sites, so variable @y@ 
would not be polluted by @1@, but two call-sites still share the same continuation and
it is still helplessness for distinguish return-flows.
TODO: do need more details to explain this example? (as in P4F paper)

@@

@f1@ and @f2@ mutually call each others, and the stack will be alternatively
pushing @f1@ and @f2@ onto the top of current stack, but not existing 
two stack components are identical in the state space.

@@

In recent years, there are great efforts \cite{vardoulakis2010cfa2, earl2012introspective, 
gilray2016pushdown, johnson2015abstracting} to achieve precise call/return 
match based on small-step AAM which is what we described in section \ref{aam}.

@@

\textbf{Pushdown for Free.}
\citeauthor{gilray2016pushdown} proposed a continuation address allocator for 
small-step abstracting abstract machine that is both easy to implement and
computational inexpensive.
The only change in code is when allocating a continuation address, not only
keep track of the entry-point expression of callee, but also hold the target environment.
The target environment is the environment extended from closure's environment
(namely @val new_env = env_c + (v -> baddr)@). All the rest things remain the same.

@@

TODO: explain the reason why it works.
Notably, this change only causes constant-factor increase in time complexity of analysis.

@@

On the other side, with the insight from Reynold's seminal paper 
\emph{Definitional interpreters for higher-order programming languages} \cite{reynolds1972definitional}
that the defined language will inherit properties
from the defining language, \citeauthor{darais2017abstracting} construct abstracting 
definitional interpreters (ADI) that automatically inherit the pushdown control-flow 
property from its defining language.

TODO: connection to this paper.
TODO: although they establish pushdown control-flow analysis in different ways, 
is there a correspondence between different methods?
